### 2012-11-28 inst/examples/policycosts/policycosts_writeup.Rmd
cpu settings for zero

This can take a while, so we use explicit parallelization, 
``` {r  parallel}
require(snowfall)
sfInit(cpu=2, parallel=T)
sfLibrary(pdgControl)
sfExportAll()
````

>>>>

This can take a while, so we use explicit parallelization, 
``` {r  parallel}
require(snowfall)
sfInit(cpu=8, parallel=T)
sfLibrary(pdgControl)
sfExportAll()
````
